\documentclass[a4paper,11pt]{article}
\include{../../../latex_headers/lab_header}


% ---------------------------------- Document ----------------------------------
\begin{document}
\pagenumbering{arabic}

\begin{center}
{\Large CMPUT 350 Lab 8 Exercise Problems}
\end{center}

\labrules{g++ -Wall -Wextra -O -g -std=c++17 ...}{Triang2.cpp}{8}


1. [29 marks]

In this exercise you will complete a program that generates a Delaunay
triangulation by first incrementally generating a triangulation for n points
in a bounding rectangle and then flipping edges to increase the minimum
interior angle locally.

\bigskip

To get started, download all files into a new folder - individually by
right-click-save or by extracing all files from \texttt{lab8\_ex.zip}

\bigskip

We provide a driver (\texttt{disp.cpp}) that animates the process using OpenGL and a
working executable (\texttt{disp.lab}) as reference. Please note that after downloading
this file you have to set its executable flag like so: \texttt{chmod +x disp.lab}

\bigskip

Our driver accepts command line parameters that may be useful for testing. Run
\texttt{./disp.lab -h} to see a list. To reproduce program runs set seed to != 0 (see test
scripts \texttt{test\_diag}, \texttt{test\_fast}, \texttt{test\_slow}).

\bigskip


Your task is to complete functions in \texttt{Triang2.cpp} in which we also provide
hints. Don't change any other file because you'll only submit \texttt{Triang2.cpp}.

\bigskip


Start by reading \texttt{Triang.h} and \texttt{Triang.cpp}, which contain most of the
implementations already. We encourage you to use our implemented functions in
your solutions.

\bigskip


To compile your program use \texttt{make}

You may change \texttt{disp.cpp} for testing your functions

You can run \texttt{./disp} from a remote machine provided 

\begin{enumerate}
    \item you use x2go, or
    \item you are using a UNIX environment on your computer (e.g., MacOS, or hosting
        Ubuntu on Windows + installing an X-Window server)
    \item you have an X-Window server running on your own computer and use ssh -X
    ... to connect to a lab machine (-X forwards X-Window connections, try to
    run "xeyes" on the lab machine to see if it works)
\end{enumerate}

\bigskip

\textbf{IMPORTANT}: Please note that any crashes you might experience while testing
your functions are most likely caused by your code, which is assumed to be
correct by the Delaunay triangulation code that calls them. In such cases, we
suggest to test your functions independently.
\end{document}